\chapter{Related Work}
\label{chap:RelatedWork}

\section{Production Order Release in SAP S/4HANA}
The release of a production order marks the transition from planning to execution in manufacturing. Before release, supervisors must ensure that all required components are available (\emph{availability checks}) and that machines and labor have sufficient free capacity (\emph{capacity evaluation}). In SAP S/4HANA Public Cloud, these validations are often performed manually across multiple applications, which is time-consuming and error-prone. Although automation can improve efficiency, current systems still assume that the BOM is complete and up to date—an assumption that rarely holds in practice and complicates automated decision-making \cite{sapprodrelease2025}.

\section{SAP Joule}
Joule is SAP’s generative AI copilot, designed to support business users across different domains of the intelligent enterprise \cite{sapjoule2025}. It provides natural language interfaces, decision recommendations, and integration with enterprise data. In the context of manufacturing, Joule can be extended with custom functions that access transactional data through OData Application Programming Interfaces (APIs). These so-called \emph{Joule Functions} enable developers to implement domain-specific logic, such as retrieving stock levels or proposing alternative materials. SAP provides sample repositories to illustrate how Joule Functions can be created and embedded into workflows, lowering the barrier for extending AI-driven support in S/4HANA.

\section{SAP Agent Builder}
The SAP Agent Builder framework allows the creation and orchestration of AI agents within the SAP ecosystem. Agents can encapsulate business logic, interact with core S/4HANA modules, and cooperate with Joule to deliver contextual recommendations. In manufacturing scenarios, Agent Builder offers a structured way to automate repetitive tasks such as production order release checks, while ensuring compliance with enterprise security and governance standards. Previous work has demonstrated the potential of multi-agent systems in industrial settings \cite{wuest2016}, and Agent Builder brings these concepts into the SAP Public Cloud. For this project, it serves as the foundation for developing an AI-powered Production Order Release Agent that can dynamically suggest alternatives and guide supervisors in decision-making.